Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
pass on RQ1

\section{Dynamic Slicing (\ds{})}
%\label{sec:background}
\label{sec:slicing}

Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest. Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality. Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

@@

\begin{table}[h]
  \small  
  \centering
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{lrrr}
    \toprule
    Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
    \midrule
    \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
    \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
    %      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
    \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
    \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
    \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
    \bottomrule
  \end{tabular}
  \caption {Characterization of \dfj{} subjects.}
  \label{tab:df4j}
\end{table}
\normalsize

@@

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used 5 and
10 as the values of $k$. The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.

@@

\Mar{--------------------------- estou aqui}

This section addresses the research questions we posed.

@@

\subsubsection{RQ1: \textit{\rqone}}
\label{rq:1}

This subsection aims to report the performance of the \ds{} technique on slicing de
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top
$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction
of $30.23\%$ in the projects considered in our study.

\begin{table}[H]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{5}  & \combpar{10} \\
		\midrule

        \lang{}            & 1.40\% & 31.46\%\\
        \cmath{}           & 10.30\% & 12.34\%\\
        %\closure{}          &  & \\
		\chart{}			& 59.30\% & 53.64\% \\
        \jtime{}            & 17.27\% & 32.02\%\\
        \mockito{}          & 16.54\% & 21.67\%\\

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction for $k=5$ and $k=10$}
	\label{tab:red}
\end{table}
\normalsize

@@

Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. $33$ of the $260$
faulty versions are cases whose faulty statements decreased in the ranking list due to being a fault of omission case or due to limitations regarding the test design which \ds{} could not handle. Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases that are result of the limitations mentioned before. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
Instead, if $k=10$ is considered the proposed approach returns an improvement of
$6.1$ on the rank mean of all faulty statements.
This $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none. Yet,
if we only consider the faults ($116$) where there was improvement in at least 
one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for 
$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is very significant.

Although this dataset has more than $50\%$ of fault of omissions,
our simple slicing approach was capable of improving the ranking of $95$ faults for
$k=5$ and $115$ faults for $k=10$. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With $99\%$ of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test,
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With $99\%$ of confidence, the results show that the
distributions are distinct. To understand which techniques perform differently - i.e., \textit{Does \combpar{10} perform differently than \sfl{}$^{10}$} -
we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all pairs of techniques. Each square represents the significance between the correspondent techniques, i.e., if it is significant it means that the techniques perform differently. With $95\%$ of confidence, it is possible to confirm that the performance of all techniques is different expect when comparing \combpar{5} with \combpar{10}.

>>>>

\section{Dynamic Slicing (\ds{})}
%\label{sec:background}
\label{sec:slicing}
\Sof{Falar de model-based diagnosis}\Rui{important to connect to the AI
community --- we are submitting this to ijcai.}
Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest. Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality. Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

@@

\begin{table}[h]
  \small
  \centering
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{lrrr}
    \toprule
    Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
    \midrule
    \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
    \cmath{}           & 306,276  & 26,797 & 104     \\   %\comments{& 177   &  -}\\
    %      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
    \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
    \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
    \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
    \bottomrule
  \end{tabular}
  \caption {Characterization of \dfj{} subjects.}
  \label{tab:df4j}
\end{table}
\normalsize

@@

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used 5 and
10 as the values of $k$. The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.
\Rui{we should say that k follows from typical SFL metrics (top k)}

@@

This section answers the research questions.

@@

%% This subsection aims to report the performance of the \ds{} technique
%% on slicing de faults of $5$ \dfj{} projects.

\subsubsection{\label{rq:1}RQ1: \textit{\rqone}}

A necessary but insufficient condition for improvement of fault
localization with \comb{} is that dynamic slicing eliminates a high
amount of code in the best ranked files. Table \ref{tab:red} shows, as
percentages, the average reduction on the sum of top file sizes
obtained with dynamic slicing for different values of
$k$.\Mar{$\leftarrow$sofia, please check.} Overall, results indicate
that dynamic slicing substantially reduces the size of highly-ranked
files. \Mar{sofia, it would be more convincing if you (additionally)
  show reduction wrt to the the parts of the file that are covered.}

%% obtained for each project after slicing the top $5$ and
%% $10$ of classes comprising the highest faulty statements. We observed
%% a reduction of $30.23\%$ in the projects considered in our study.

\begin{table}[H]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

        \lang{}            & 1.40 & 31.46\\
        \cmath{}           & 10.30 & 12.34\\
        %\closure{}          &  & \\
		\chart{}			& 59.30 & 53.64 \\
        \jtime{}            & 17.27 & 32.02\\
        \mockito{}          & 16.54 & 21.67\\

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction, as percentages. Higher is better.}
	\label{tab:red}
\end{table}
\normalsize

@@

Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. $33$ of the $260$
faulty versions are cases whose faulty statements decreased in the ranking list due to being a fault of omission case or due to limitations regarding the test design which \ds{} could not handle. Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases that are result of the limitations mentioned before. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
Instead, if $k=10$ is considered the proposed approach returns an improvement of
$6.1$ on the rank mean of all faulty statements.
This $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none. Yet,
if we only consider the faults ($116$) where there was improvement in at least
one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for
$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is significant.

Although this dataset has more than $50\%$ of fault of omissions,
our simple slicing approach was capable of improving the ranking of $95$ faults for
$k=5$ and $115$ faults for $k=10$. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With $99\%$ of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With $99\%$ of confidence, the results show that the
distributions are distinct. To understand which techniques perform differently - i.e., \textit{Does \combpar{10} perform differently than \sfl{}$^{10}$} -
we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all pairs of techniques. Each square represents the significance between the correspondent techniques, i.e., if it is significant it means that the techniques perform differently. With $95\%$ of confidence, it is possible to confirm that the performance of all techniques is different expect when comparing \combpar{5} with \combpar{10}.
